elasticnet

### 2022-06-06 analysis/benchmarks.Rmd
fix: bootstraping elastic net

```{r benchmarks_plot_c_harrell, fig.width = 18}
m <- agg[, max(harrell), by = task_id]
autoplot(bmrk_results) +
    geom_boxplot(aes(fill = learner_id)) +
    geom_jitter(position = position_jitter(0.2)) +
    scale_fill_viridis(discrete = TRUE) +
    geom_hline(
        aes(yintercept = V1), linetype = "dashed", color = "red", data = m
    ) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

```{r benchmarks_plot_c_uno, fig.width = 18}
autoplot(
    bmrk_results,
    measure = msr("surv.cindex", id = "uno", weight_meth = "G2")) +
    geom_boxplot(aes(fill = learner_id)) +
    geom_jitter(position = position_jitter(0.2)) +
    scale_fill_viridis(discrete = TRUE) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

@@

```{r benchmarks_aggr_plot_c_harrell}
autoplot(bmrk_aggr, type = "box", meas = "harrell") +
    geom_boxplot(aes(fill = learner_id)) +
    geom_jitter(position = position_jitter(0.2)) +
    scale_fill_viridis(discrete = TRUE) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

```{r benchmarks_aggr_plot_c_uno}
autoplot(bmrk_aggr, type = "box", meas = "uno") +
    geom_boxplot(aes(fill = learner_id)) +
    geom_jitter(position = position_jitter(0.2)) +
    scale_fill_viridis(discrete = TRUE) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

>>>>

```{r benchmarks_plot_c_harrell, fig.width = 18, fig.height = 12}
m <- agg[, max(harrell), by = task_id]
autoplot(bmrk_results) +
    geom_boxplot(aes(fill = learner_id)) +
    geom_jitter(position = position_jitter(0.2)) +
    scale_fill_viridis(discrete = TRUE) +
    geom_hline(
        aes(yintercept = V1), linetype = "dashed", color = "red", data = m
    )
```

```{r benchmarks_plot_c_uno, fig.width = 18, fig.height = 12}
autoplot(
    bmrk_results,
    measure = msr("surv.cindex", id = "uno", weight_meth = "G2")) +
    geom_boxplot(aes(fill = learner_id)) +
    geom_jitter(position = position_jitter(0.2)) +
    scale_fill_viridis(discrete = TRUE)
```

@@

```{r benchmarks_aggr_plot_c_harrell}
autoplot(bmrk_aggr, type = "box", meas = "harrell") +
    geom_boxplot(aes(fill = learner_id)) +
    geom_jitter(position = position_jitter(0.2)) +
    scale_fill_viridis(discrete = TRUE)
```

```{r benchmarks_aggr_plot_c_uno}
autoplot(bmrk_aggr, type = "box", meas = "uno") +
    geom_boxplot(aes(fill = learner_id)) +
    geom_jitter(position = position_jitter(0.2)) +
    scale_fill_viridis(discrete = TRUE)
```

### 2022-06-06 analysis/elasticnet.Rmd
fix: bootstraping elastic net

```{r elasticnet_setup, message = FALSE}
library("targets")
library("ameld")
library("viridisLite")
tar_load(arcvob)
tar_load(bootrcv)
tar_load(bootarcv)
#tar_load(bootarcv9)
tar_load(amelddata)
tar_load(ameldcfg)
tar_load(zlog_data)
```

@@

@@

@@

```{r bootarcv9}
#a <- c(table(sapply(bootarcv9$models, function(m)m$fit$alpha)))
#plot(bootarcv9 , what = "calibration")
#plot(bootarcv9, what = "selected")
#plot_dots(a, main = "Selected Alpha Values")
```

>>>>

```{r elasticnet_setup, message = FALSE}
library("targets")
library("ameld")
library("viridisLite")
tar_load(arcvob)
tar_load(bootrcv)
tar_load(bootarcv)
tar_load(bootarcv7)
tar_load(bootarcv9)
tar_load(bootrcv.woICA)
tar_load(amelddata)
tar_load(ameldcfg)
tar_load(zlog_data)
```

@@

## bootrcv.woICA

```{r bootrcv.woICA}
plot(bootrcv.woICA, what = "calibration")
plot(bootrcv.woICA, what = "selected", cex = 0.5)
```

@@

## arcv7.glmnet

```{r bootarcv7}
a <- c(table(sapply(bootarcv9$models, function(m)m$fit$alpha)))
plot(bootarcv7 , what = "calibration")
plot(bootarcv7, what = "selected")
plot_dots(a, main = "Selected Alpha Values")
```

@@

```{r bootarcv9}
a <- c(table(sapply(bootarcv9$models, function(m)m$fit$alpha)))
plot(bootarcv9 , what = "calibration")
plot(bootarcv9, what = "selected")
plot_dots(a, main = "Selected Alpha Values")
```
